The ``Dark Side'' of Phylogenetic Comparative Methods$^\dag$

### 2015-04-17 Manuscript/dark.tex
Changed locations of figures
Small changes

\title{The ``Dark Side'' of Phylogenetic Comparative Methods$^\dag$}
\author{
  Natalie Cooper$^{1,2,*}$, Matthew W. Pennell$^{3}$ \\
  and Richard G. FitzJohn$^{4}$ 
  %Cecile An\'{e}$^{2}$, Wayne Maddison$^{3}$,\\  Gavin H. Thomas$^{5}$, April Wright$^{6}$,\\
}
\date{}
\affiliation{\noindent{\footnotesize

 % $^2$ Wisconsin\\
 % $^3$ UBC\\
 % $^5$ Sheffield\\
 % $^6$ Austin\\
  $^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
  $^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
  $^3$ Institute for Bioinformatics and Evolutionary Studies, University of Idaho, Moscow, ID 83844, U.S.A.\\
  $^4$ Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia. \\
  $^*$ Corresponding author: ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland. 
       Fax: +353 1 677 8094; Tel: +353 1 896 1926.\\
  $^\dag$This paper is based on a Society of Systematic Biologists symposium at Evolution 2014, in Raleigh NC.\\
}}

>>>>

\title{The ``Dark Side'' of Phylogenetic Comparative Methods$^\dag$}
\author{
  Natalie Cooper$^{1,2,*}$ and Richard G. FitzJohn$^{4}$ 
  %Cecile An\'{e}$^{2}$, Wayne Maddison$^{3}$,\\  Gavin H. Thomas$^{5}$, April Wright$^{6}$,\\
}
\date{}
\affiliation{\noindent{\footnotesize

 % $^2$ Wisconsin\\
 % $^3$ UBC\\
 % $^5$ Sheffield\\
 % $^6$ Austin\\
  $^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
  $^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
  $^3$ Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia. \\
  $^*$ Corresponding author: ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland. Fax: +353 1 677 8094; Tel: +353 1 896 1926.\\
  $^\dag$This paper is based on a Society of Systematic Biologists symposium at Evolution 2014, in Raleigh NC.\\
}}
